Malware Detection Via Machine Learning

### 2016-12-02 project_report/main.tex
More intro, until malwr description.

@@

\todo[inline]{talk about machine learning, how it can be applied with behavioral analysis}
\hfill \break

>>>>

Having to run samples in order to extract dynamic information poses the problem of infecting the system running the samples. One way to prevent this is to use a sandbox environment, which is a security mechanism to isolate running programs. Using a sandbox environment closely relates to computer virtualization.

To provide users the possibility to check files without running the risk of being infected, online services allow users to submit files which are then run in a sandbox environment.

An example of such service is malwr. Malwr takes user submissions and runs them in a sandbox environment, specifically Cuckoo Sandbox, providing static and dynamic information about the sample, as well as checking if the file is known in VirusTotal, a similar service that also checks if the submission is known in different antivirus solutions. Malwr was first launched in April 2013 and contains nearly 700 000 analyses.

@@

\todo[inline]{brief look on what malwr does and provides}
\todo[inline]{re-focus on high amount of malware, difficulty of having to run all samples and check}
\todo[inline]{propose machine learning as a solution to deal with the high amounts of data}
\hfill \break
